Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-23 paper/aldebaran.tex

We have determined the stellar properties of Aldebaran with the additional constraint of \numax determined from our analysis here.  The details of the stellar modelling are presented in detail in \ref{sec:mod}.  We have considered the impact of our additional \numax constraint and run our analysis for different sets of spectroscopic estimates.  For final values we adopt the Sheffield et al. (2012) b spectroscopic solution as being 'middle of the road' estimates.  For the analysis without constraint on \numax we find estimates of the stellar properties as $M = 1.43^{+0.24}_{-0.2} \, \mathrm{M_{\odot}}$ and age $4.86^{3.56}_{2.04} \, \rm Gyr$.  With the inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and age $6.38^{1.42}_{1.12} \, \rm Gyr$.  It is clear that the addition of \numax provides substantially more precise estimates of Mass and Age.

>>>>

We have determined the stellar properties of Aldebaran with the additional constraint of \numax determined from our analysis here.  The details of the stellar modelling are presented in detail in \ref{sec:mod}.  We have considered the impact of our additional \numax constraint and run our analysis for different sets of spectroscopic estimates.  For final values we adopt the Sheffield et al. (2012) b spectroscopic solution as being 'middle of the road' estimates.  For the analysis without constraint on \numax we find estimates of the stellar properties as $M = 1.27^{+0.24}_{-0.2} \, \mathrm{M_{\odot}}$ and age $4.86^{3.56}_{2.04} \, \rm Gyr$.  With the inclusion of \numax we find $M = 1.16^{+0.07}_{-0.07} \, \mathrm{M_{\odot}}$ and age $6.38^{1.42}_{1.12} \, \rm Gyr$.  It is clear that the addition of \numax provides substantially more precise estimates of Mass and Age.
